Torontonians Prefer to Get Married in the Warmer Half of the Year

### 2024-01-22 outputs/paper/paper.qmd
changed abstract

---
title: "Getting Hitched: Torontonians Prefer to Get Married During Warm Weather"
author: Diana Liu
thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Analysis-of-Toronto-Marriages"
date: 25 January 2024
abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months. By dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March), the number of marriage licenses obtained in Toronto increase significantly during warm months, supporting the hypothesis that Torontonians prefer to get married during warm weather."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

*** Discussion Section

>>>>

---
title: "Torontonians Prefer to Get Married in the Warmer Half of the Year"
author: Diana Liu
thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Analysis-of-Toronto-Marriages"
date: 25 January 2024
abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months, dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March). We found that the number of marriage licenses obtained in 2022 increased by 117% between cold and warm months and 68% in 2023. This supports our hypothesis that Torontonians prefer to get married during the warmer half of the year."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

*insert discussion in intro
